\documentclass[a4paper,12pt]{article}

\input{packages}
\input{bibsetup}
\input{name}
\input{utils}

% ------ dynamic web references -------------------------------

%this needs to come before the acronyms
\newtoggle{expliciturl}
\toggletrue{expliciturl}
\newcommand{\dynhref}[2]{%
  \iftoggle{expliciturl}{%
    #2 \footnote{\href{http://#1}{\detokenize{#1}}}%
  }{%
    \href{http://#1}{#2}%
  }%
}

%acronym packaged loaded inside
\input{acronyms}

% ------ home or work address -------------------------------

\newtoggle{homecontact}
% \togglefalse{homecontact}
\toggletrue{homecontact}
\newcommand{\homecv}[2]{\iftoggle{homecontact}{#1}{#2}}

% ------ academic links -------------------------------

\newtoggle{academicweb}
% \togglefalse{academicweb}
\toggletrue{academicweb}
\newcommand{\academicwebcv}[2]{\iftoggle{academicweb}{#1}{#2}}

% ------ professional cv, false for academic cv -------------------------------

\newtoggle{professionalcv}
\togglefalse{professionalcv}
% \toggletrue{professionalcv}
\newcommand{\procv}[2]{\iftoggle{professionalcv}{#1}{#2}}

% ------ teaching experience -------------------------------

\newtoggle{teaching}
\togglefalse{teaching}
% \toggletrue{teaching}
\newcommand{\teachingcv}[2]{\iftoggle{teaching}{#1}{#2}}

% ------ summary text -------------------------------

\newtoggle{summary}
\togglefalse{summary}
% \toggletrue{summary}
\newcommand{\summarycv}[2]{\iftoggle{summary}{#1}{#2}}

% ------ Customizations --------------------------------------------------------

% % Customize page headers
% \pagestyle{myheadings}
% \markright{\it{\name}}

% Don't indent paragraphs.
\setlength\parindent{0pt}

% ------ Start --------------------------------------------------------

\begin{document}

\centerline
{\huge \rm \textbf \name}

\procv{}{\input{affiliation}}

% ------- Personal data ---------------------------------------------------

\begin{cvsection}{Personal Information}

{\bf Full Name:} & Jo\~ao~Greg\'orio~de~Teixeira~da~Encarna\c c\~ao \\
{\bf Birth:} & $25^{\sf th}$ of February 1977 at Funchal, Portugal \\
{\bf Nationality:} &  Portuguese\\

\homecv{%
  {\bf Marital Status:} & Single \\
  {\bf Address:}   & 4303 Duval Street 302
                    78751, Austin Texas, USA\\
  {\bf Telephone:} & +1 512 765 1351\\
  {\bf Email:}     & \href{mailto:j_encarnacao@yahoo.com}{j\_encarnacao@yahoo.com}\\
}{%
  {\bf Address:}   & 3925 W Braker Lane\newline
                     Ste 200 - WPR 2.9076\newline
                     Austin TX 78759-5316, \ac{USA}\\
  {\bf Telephone:} & +1 (512) 232-6897\\
  {\bf Email:}     & \href{mailto:teixeira@csr.utexas.edu}{teixeira@csr.utexas.edu}\\
}%
\academicwebcv{%
  {\bf Web:}       & \dynhref{directory.utexas.edu/index.php?q=joao+encarnacao}{University of Texas},
                     \dynhref{www.tudelft.nl/en/staff/j.g.deteixeiradaencarnacao-2/}{TU Delft},
                     \dynhref{nl.linkedin.com/in/joaoencarnacao}{LinkedIn},
                     \dynhref{www.researchgate.net/profile/Joao_Encarnacao2}{ResearchGate},
                     \dynhref{scholar.google.com/citations?user=k2liFwQAAAAJ}{Google Scholar},
                     \dynhref{orcid.org/0000-0001-6824-2733}{ORCID},
                     \dynhref{www.mendeley.com/profiles/joao-encarnacao4/}{Mendeley},
                     \dynhref{www.scopus.com/authid/detail.uri?authorId=15135565900}{SCOPUS},
                     \dynhref{publons.com/a/782170/}{Publons},
                     \dynhref{github.com/jgte}{GitHub}\\
}{%
  {\bf Web:}       & \dynhref{nl.linkedin.com/in/joaoencarnacao}{LinkedIn},
                     \dynhref{github.com/jgte}{GitHub}\\
}

\end{cvsection}

% ------- Summary ---------------------------------------------------

\summarycv{\input{summary}}{}

% ------- Education ---------------------------------------------------

\begin{cvsection}{Education}

2015 &
  \begin{itti}
    \item \textbf{PhD in Space Geodesy}
    \item \acf{GRS}, \acf{TUD}
    \item Dissertation: \dynhref{tinyurl.com/SatGrav}{\emph{Next-generation satellite gravimetry for measuring mass transport in the Earth system}}
    %TODO: fix these URLs
    \item Promotor: \dynhref{www.tudelft.nl/en/ceg/over-faculteit/departments/geoscience-remote-sensing/staff/scientific-staff/profdr-ing-habil-r-roland-klees/}{Prof. Dr-Ing. habil. Roland Klees}
    \item Supervisor: \dynhref{www.tudelft.nl/citg/over-faculteit/afdelingen/geoscience-remote-sensing/staff/scientific-staff/dr-pg-pavel-ditmar/}{Dr. Ir. Pavel Ditmar}
  \end{itti}\\


2004 &
  \begin{itti}
    \item \textbf{Master of Sciences in Aerospace Engineering}
    \item \acf{AS}, \ac{TUD}
    \item Final Thesis: \emph{Numerical Simulation of Launch Vehicles}
    \item Supervisor: \dynhref{www.tudelft.nl/en/staff/b.a.c.ambrosius}{Prof. Ir. B.A.C. Ambrosius}
  \end{itti}\\

2000 &
  \begin{itti}
    \item \textbf{\acf{Lic.} in Aerospace Engineering}
    \item \acf{IST}, \acf{UTL}
    \item 5$^{\rm th}$ year concluded at \ac{TUD}, through the \dynhref{www.erasmusprogramme.com}{ERASMUS program}
    \item Report: \emph{Optimum Aerodynamic Shape for a High Altitude Long Endurance Aerostatic Platform}
    \item Supervisor: Prof. Dr. Ir. Theo van Holten
  \end{itti}\\

\end{cvsection}

% \citem{Scholarships}\\
% Socrates/ERASMUS Scholarship of the European Union (September 1999 -- June
% 2000)


% % -------- Work experience --------------------------------------------

\begin{cvsection}{Academic and Research Experience}

Aug. 2016 -- present &
  \begin{itti}
    \item \textbf{Research Associate} at \acf{CSR}, \acf{UTexas}, \ac{USA}:
    \begin{ittib}
      \item Improvements in the calibration of the accelerometers on-board the \acf{GRACE} satellites, in particular in what relates to temperature effects;
      \item Determination of the (non-linear) long-term trends in the \ac{GRACE} gravity field solutions and their prediction during the \ac{GRACE}\slash\acf{GRACE-FO} gap;
      \item Time-varying gravity fields estimated from Kinematic Orbits;
      \item In-house software development in Matlab and Ruby.
    \end{ittib}
  \end{itti}\\

Sep. 2011 -- Jul. 2016 &
  \begin{itti}
    \item \textbf{Research Associate} at \ac{AS}, \ac{TUD}, the Netherlands:
    \begin{ittib}
      \item Calibration of the accelerometers on-board the Swarm satellites;
      \item Improvements in the modelling of non-conservative forces acting on satellites;
      \item Exploiting \acf{DSP} techniques to merge the measurement of non-gravitational accelerations from different sources: \acf{GPS}-driven and accelerometer observations;
      \item Time-varying gravity fields estimated from Kinematic Orbits;
      \item Research project: Assessment of Satellite Constellations for Monitoring the Variations in Earth's Gravity Field;
      \item Research project: GOCE+ Theme3: Air density and wind retrieval using \acf{GOCE} data;
      \item Research project: Development of the Swarm Level 2 Algorithms and Associated Level 2 Processing Facility;
      \item In-house software development in Fortran, Matlab and Ruby;
      \item Student supervision and mentoring.
    \end{ittib}
  \end{itti}\\

Jan. 2007 -- Dec. 2015 &
  \begin{itti}
    \item \textbf{PhD Candidate} at \ac{GRS}, \ac{TUD}, the Netherlands:
    \begin{ittib}
      \item Simulation of future gravimetric satellite missions and noise budget of low-low satellite-to-satellite tracking gravimetric data;
      \item Impact of orbit position modelling errors in the quality of satellite gravimetric data;
      \item Retrieval of the high-frequency time-variable gravity field of the Earth with numerous satellites;
      \item Research project: Assessment of a Next Generation Gravity Mission for Monitoring the Variations of Earth's Gravity Field;
      \item Research project: Monitoring and Modelling Individual Sources of Mass Distribution and Transport in the Earth System by Means of Satellites;
      \item In-house software development in Fortran and Matlab;
      \item Student supervision and mentoring.
    \end{ittib}
  \end{itti}\\


Apr. 2005 -- Nov. 2006 &
  \begin{itti}
    \item \textbf{Stress Engineer} at \dynhref{www.globaltechnics.nl/}{Global Technics}, Leiden, the Netherlands:
    \begin{ittib}
      \item Automated design (for weight and stress minimization) of fuselage panels for the Airbus A380 aircraft (in-house implementation of a tool in C++);
      \item Trainees supervision and mentoring.
    \end{ittib}
  \end{itti}\\

\procv{
6/2005 -- 7/2005 &
  \begin{itti}
    \item \textbf{Systems Engineer} at \dynhref{www.reduct.net}{Reduct}, Kontich, Belgium
  \end{itti}\\
}{}

Oct. 2004 -- Jan. 2005 &
  \begin{itti}
    \item \textbf{Aerospace Engineer} at \dynhref{www.delta-utec.com/}{Delta-Utec}, Leiden, the Netherlands:
    \begin{ittib}
      \item Contractor Work: Implementation of a Sub-Orbital Optimization Module into the Simulation Tool \emph{COLVET} (developed in-house at TU Delft).
    \end{ittib}
  \end{itti}\\

Mar. 2004 -- Apr. 2004 &
  \begin{itti}
    \item \textbf{Trainee} at the Prins Maurits Laboratorium, \dynhref{www.tno.nl/}{TNO}, the Netherlands
    \item Supervisor: Ir. Berry Sanders, Rocket Technology Research Group:
    \begin{ittib}
      \item Implementation of the Launch Vehicle Simulation and Optimisation Tool \emph{COLVET};
      \item Numerical Simulations on Laser Propulsion (appendix of MSc thesis);
      \item Collaboration with international colleagues (PT and NL) on a \acf{ESA}-funded project to determine the feasibility of Laser Propulsion.
    \end{ittib}
  \end{itti}\\

Sep. 2001 -- Dec. 2001 &
  \begin{itti}
    \item \textbf{Trainee} at \acf{ESTEC}, \ac{ESA}, Noordwijk, the Netherlands
    \item Supervisor: \dynhref{en.wikipedia.org/wiki/Wubbo_Ockels}{Prof. Wubbo Ockels}:
    \begin{ittib}
      \item Collaboration with fellow MSc colleagues on a space mission design project: \emph{Lunar Exploration with Ariane 5};
      \item Simulation of rocket ascent trajectories (implemented a 2D orbit integrator in Matlab);
      \item Optimization or rocket trajectories, thrust and attitude program, fuel consumption and payload;
      \item Preliminary lunar mission design.
    \end{ittib}
  \end{itti}\\

\end{cvsection}

\teachingcv{
\begin{cvtext}{Teaching Experience}

At TU Delft, I was required to supervise student projects of a practical nature, every year.
This means that I had to direct the work of a small group of students (7 to 9) to a particular objective.
It is an activity I enjoy doing and I see the students are enthusiastic about.
I always ask them to fill (anonymously) a short list of questions regarding their opinion of the project and my ability as instructor (these answer sheets are available if requested).
I always get encouraging and positive feedback.

My senior colleagues always grade my teaching activities as very good to excellent and I am often asked by students to support their application with recommendation letters.

In what concerns teaching large groups of students, I have given lectures to classes of about 30 students, on exceptional occasions, at the request of colleagues.

Additionally, I was a lecturer at the 2017 Summer School On Data Assimilation And Its Applications In Oceanography, Hydrology, Risk \& Safety And Reservoir Engineering (cf. \dynhref{data-assimilation.com}{data-assimilation.com}).

I value all teaching my experiences because they were extremely rewarding.

\end{cvtext}
}{}

% \iftoggle{expliciturl}{\pagebreak}{}


% % ------- Skills ------------------------------------------------------

\begin{cvsection}{Skills}

Communication: & Numerous presentations of research results (8 oral and 4 poster)\\

Teaching: & \vspace{-1.5ex}
  \begin{ittib}
    \item Student supervision in the context of individual and group assignments
    \item Introductory lectures to the practical projects
  \end{ittib}\\

Theoretical: & \vspace{-1.5ex}
  \begin{ittib}
   \item Parametric inversion
   \item Statistical analysis
   \item Stochastic modelling
   \item Spherical harmonic functions
   \item Digital signal processing
   \item Coordinate transformations\slash quaternion arithmetic
   \item Fourier analysis
 \end{ittib}\\


\procv{}{
Articles review: & Successfully completed the review of 9 scientific articles, cf. \dynhref{publons.com/a/782170/}{Publons}\\
}

Computational: & \vspace{-1.5ex}
  \begin{ittib}
    \item Algorithm development and implementation
    \item Data management, analysis and visualisation
    \item Automation, robustness, fault recovery
    \item Problem resolution\slash solution discovery\slash hacking
 \end{ittib}\\

Software: & Latex, MS Office, Git, SVN\\

Programming: & \vspace{-1.5ex}
  \begin{ittib}
    \item 1996 -- present: Bash
    \item 1998 -- present: Matlab
    \item 2002 -- present: Fortran
    \item 2006 -- 2008: C/C++
    \item 2011 -- present: Ruby
    \item 2015 -- present: Python
  \end{ittib}\\

\acp{OS}: & OSX, MS Windows, Unix/Linux \\

\end{cvsection}

% % ------- Fields of interest ------------------------------------------

\begin{cvsection}{Fields of Interest}
 Space geodesy & \\
 Earth System Science & \\
 Mathematical Modelling & \\
 Digital signal processing & \\
 Numerical Simulation & \\
 Big data & \\
 Rocket Motion and Orbital Mechanics & \\
 System Analysis and Design & \\
 Aerodynamics & \\
 Structural Mechanics & \\
\end{cvsection}


% % ------- Collaborations ------------------------------------------------------

\procv{}{
\begin{cvsection}{Collaborations}

2017 -- present &
Collaboration with Dr. Guillaume Ramillien from \acf{CNRS} and Dr. Ale\v{s} Bezd\v{e}k the \acf{ASU}  of the \acf{AVCR} to {\bf drive surface mass variations directly from \enquote{reduced} gravimetric data } (i.e. observations \enquote{cleaned} of non-gravitational and trivial gravitational effects).\\

2017 -- present &
Collaboration with Dr. Noble Hatten and Dr. Dae Lee of the \ac{CSR}. \ac{UTexas} for the {\bf development of a CubeSat architecture that replicates the gravimetric capabilities of the \ac{GRACE} satellites}.\\

% 2016 -- present &
% International collaboration with Prof. Luis Rocha of \acf{UMinho} and Dr. Dae Lee of the \ac{CSR}, \ac{UTexas} for the {\bf development of a \ac{MEMS}-based space accelerometer as a first step towards the nano-gravimetric satellite framework}.\\

2015 -- present &
International collaboration with
Prof. Torsten Mayer-G\"{u}rr of the \acf{IfG} of the \acf{TUG},
Dr. Ale\v{s} Bezd\v{e}k of the \ac{ASU}  of the \acf{AVCR},
Prof. Adrian J\"{a}ggi of the \acf{AIUB},
Prof. Pieter Visser of the \dynhref{www.lr.tudelft.nl}{Aerospace Faculty} of the \ac{TUD} and
Prof. C.K. Shum of the \acf{SES} of the \acf{OSU}
for the {\bf study of the time-variable gravity field of the Earth estimated from GPS data collected by the \dynhref{earth.esa.int/web/guest/missions/esa-operational-eo-missions/swarm}{Swarm Satellite mission}}. Within the scope of this project, we submitted a grant application with very positive reviews (Ref. ESA AO/1-7927/14/NL/MP), and have recently been awarded funding under the \dynhref{tinyurl.com/SwarmGrav}{ITT posted by the \ac{ESA}-funded a\ac{DISC} consortium}\\

2014 -- present &
Collaboration with \ac{TUD} on the \dynhref{doptrack.tudelft.nl}{DopTrack project}, consisting of a {\bf satellite tracking radio station that exploits the Doppler effect}; co-initiated and promoted the project, secured departmental funding, selected and assembled the hardware, developed software, engaged students and mentored practical undergraduate projects.\\

\end{cvsection}
}

% % -------- Research Projects ----------------------------------------------------

\procv{}{
\begin{cvsection}{Research Projects}
2013 -- 2015  & Assessment of Satellite Constellations for Monitoring the Variations in Earth's Gravity Field (ESA contract 4000108663/13/NL/MV) \\
2013          & GOCE+ Theme3: Air density and wind retrieval using GOCE data (ESA contract 400010284/11/NL/EL)\\
2011 -- 2016  & Development of the Swarm Level 2 Algorithms and Associated Level 2 Processing Facility (ESA Contract 4000102140/10/NL/JA)\\
2010          & Assessment of a Next Generation Gravity Mission for Monitoring the Variations of Earth's Gravity Field (ESTEC contract 22643/09/NL/AF)\\
2008          & Monitoring and Modelling Individual Sources of Mass Distribution and Transport in the Earth System by Means of Satellites (ESA contract 20403) \\
\end{cvsection}
}

% % -------- Publications ----------------------------------------------------

\procv{}{\input{publications}}

% % ------- Languages ------------------------------------------------------

\begin{cvtext}{Languages}
\begin{tabular}{
l
>{\centering\arraybackslash}m{3cm}
>{\centering\arraybackslash}m{3cm}
>{\centering\arraybackslash}m{3cm}}
   & Speaking & Reading & Writing \\
\hline
Portuguese & \multicolumn{3}{c}{mother tongue}  \\
English\footnote{holder of the \dynhref{www.cambridgeenglish.org/exams/proficiency/index.aspx}{Certificate of Proficiency in English}}    & excellent & excellent & excellent \\
Spanish    & good & good & fair \\
Italian    & good & good & fair \\
Dutch      & fair & fair & limited \\
French     & fair & fair & limited \\
\hline
\end{tabular}
\end{cvtext}

% % ------- Personal development ------------------------------------------------------

\begin{cvsection}{Personal development}

Sep. 2015 & Scientific Writing, Sören Johnson, \ac{TUD}\\

Jul. 2017 & Leading without formal authority, Emil Kresl, \ac{UTexas}\\

Jul. 2017 & Meeting effectiveness, Emil Kresl, \ac{UTexas}\\

Sep. 2017 & Dealing with Difficult People, Jeff Stellmach, \ac{UTexas}\\

Sep. 2017 & Conflict Management Foundations, Kimberly Sullivan, \ac{UTexas}\\

\end{cvsection}

% % -------- Other Activities --------------------------------------------

\begin{cvsection}{Sports}
1991 -- 2009 & Basketball \\
April 2006   & Finalist of the \dynhref{www.fortismarathonrotterdam.nl/}{26th International Fortis Marathon of Rotterdam}\\
September 2016 - present & Sailing\\
\end{cvsection}

\begin{cvsection}{Other Activities}
1991 -- 2001 & Scout at the 92$^{nd}$ Scout-group of the \dynhref{www.aep.pt}{Association of Portuguese Escoteiros}\\
1993 -- present & Radio Amateur, call sign CT3IU, class B\\
\procv{1996 -- present & Drivers Licence \\}{}
\end{cvsection}

% % -------- References --------------------------------------------

% \pagebreak

\input{references}

\vfill
The \dynhref{jgte.github.io/cv/cv_jgte.pdf}{PDF} and \dynhref{jgte.github.io/cv/cv_jgte_print.pdf}{print-ready} versions this document are available on-line.

\label{endpage}
\end{document}
